---
title: "bargraphsfordataed"
author: "Nathalie Huerta"
date: "7/17/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
#Sky helped me to run code 
library(dplyr)
Suspension11 <- read.csv(file = "Suspension2011-12.csv", header = T) #imports the data 
#this is the data for 2012-2013
Suspension12 <- read.csv(file= "Suspension2012-13.csv", header = T) #imports the data 
#this is the data for 2013-14
Suspension13 <- read.csv(file= "Suspension2013-14.csv", header = T) #imports the data 
#this is the data for 2014-2015
Suspension14 <- read.csv(file= "Suspension2014-15.csv", header = T) #imports the data 
#this is the data for 2016-2017
Suspension15 <- read.csv(file= "Suspension2015-16.csv", header = T)
Suspension16 <- read.csv(file= "Suspension2016-17.csv", header = T) #imports the data 
```

#Steps to Build the bar graph for Gender 
# ```{r}
# county_GMcount11 <- filter(Suspension11, Suspension11$reportingcategory =="GM")
# 
# county_GFcount11 <- filter(Suspension11, Suspension11$reportingcategory =="GF")
# 
# GMcounty11 <- county_GMcount11[c(2:59), c(1,6,10,12)]
# GMcounty11
# 
# SuspensionMales11 <- sum(as.numeric(as.character(GMcounty11$totalsuspensions)))
# SuspensionMales11
# 
# GFcounty11 <- county_GFcount11[c(2:59), c(1,6,10,12)]
# GFcounty11
# 
# SuspensionFemales11 <- sum(as.numeric(as.character(GFcounty11$totalsuspensions)))
# SuspensionFemales11
# 
# #---------------------------------------------------------------------------------------------------
# 
# county_GMcount12 <- filter(Suspension12, Suspension12$reportingcategory =="GM")
# 
# county_GFcount12 <- filter(Suspension12, Suspension12$reportingcategory =="GF")
# 
# GMcounty12 <- county_GMcount11[c(2:59), c(1,6,10,12)]
# GMcounty12
# 
# SuspensionMales12 <- sum(as.numeric(as.character(GMcounty12$totalsuspensions)))
# SuspensionMales12
# 
# GFcounty12 <- county_GFcount12[c(2:59), c(1,6,10,12)]
# GFcounty12
# 
# SuspensionFemales12 <- sum(as.numeric(as.character(GFcounty12$totalsuspensions)))
# SuspensionFemales12
# 
# #---------------------------------------------------------------------------------------------------
# 
# county_GMcount13 <- filter(Suspension13, Suspension13$reportingcategory =="GM")
# 
# county_GFcount13 <- filter(Suspension13, Suspension13$reportingcategory =="GF")
# 
# GMcounty13 <- county_GMcount13[c(2:59), c(1,6,10,12)]
# GMcounty13
# 
# SuspensionMales13 <- sum(as.numeric(as.character(GMcounty13$totalsuspensions)))
# SuspensionMales13
# 
# GFcounty13 <- county_GFcount13[c(2:59), c(1,6,10,12)]
# GFcounty13
# 
# SuspensionFemales13 <- sum(as.numeric(as.character(GFcounty13$totalsuspensions)))
# SuspensionFemales13
# 
# #---------------------------------------------------------------------------------------------------
# 
# county_GMcount14 <- filter(Suspension14, Suspension14$reportingcategory =="GM")
# 
# county_GFcount14 <- filter(Suspension14, Suspension14$reportingcategory =="GF")
# 
# GMcounty14 <- county_GMcount14[c(2:59), c(1,6,10,12)]
# GMcounty14
# 
# SuspensionMales14 <- sum(as.numeric(as.character(GMcounty14$totalsuspensions)))
# SuspensionMales14
# 
# GFcounty14 <- county_GFcount14[c(2:59), c(1,6,10,12)]
# GFcounty14
# 
# SuspensionFemales14 <- sum(as.numeric(as.character(GFcounty14$totalsuspensions)))
# SuspensionFemales14
# 
# #-------------------------------------------------------------------------------------------------
# 
# county_GMcount15 <- filter(Suspension15, Suspension15$reportingcategory =="GM")
# 
# county_GFcount15 <- filter(Suspension15, Suspension15$reportingcategory =="GF")
# 
# GMcounty15 <- county_GMcount15[c(2:59), c(1,6,10,12)]
# GMcounty15
# 
# SuspensionMales15 <- sum(as.numeric(as.character(GMcounty15$totalsuspensions)))
# SuspensionMales15
# 
# GFcounty15 <- county_GFcount15[c(2:59), c(1,6,10,12)]
# GFcounty15
# 
# SuspensionFemales15 <- sum(as.numeric(as.character(GFcounty15$totalsuspensions)))
# SuspensionFemales15
# 
# #--------------------------------------------------------------------------------------------
# 
# county_GMcount16 <- filter(Suspension16, Suspension16$reportingcategory =="GM")
# 
# county_GFcount16 <- filter(Suspension16, Suspension16$reportingcategory =="GF")
# 
# GMcounty16 <- county_GMcount16[c(2:59), c(1,6,10,12)]
# GMcounty16
# 
# SuspensionMales16 <- sum(as.numeric(as.character(GMcounty16$totalsuspensions)))
# SuspensionMales16
# 
# GFcounty16 <- county_GFcount16[c(2:59), c(1,6,10,12)]
# GFcounty16
# 
# SuspensionFemales16 <- sum(as.numeric(as.character(GFcounty16$totalsuspensions)))
# SuspensionFemales16
# ```
# 
# ```{r}
# #install.packages("scales")
# library(scales)
# library(ggplot2)
# Female <-c(SuspensionFemales11, SuspensionFemales12, SuspensionFemales13, SuspensionFemales14, SuspensionFemales15, SuspensionFemales16)
# 
# Male <- c(SuspensionMales11, SuspensionMales12, SuspensionMales13, SuspensionMales14, SuspensionMales15, SuspensionMales16)
# 
# Years <- c(2011:2016)
# 
# FemTot <- data.frame(Years, Female)
# names(FemTot) <- c("Years","Total")
# FemTot$Gender <- "Female"
# 
# MaleTot <- data.frame(Years, Male)
# names(MaleTot) <- c("Years", "Total")
# MaleTot$Gender <- "Male"
# 
# GenTot <- rbind(FemTot, MaleTot)
# 
# GenTot$Years[GenTot$Years == 2011] <- "2011-12"
# GenTot$Years[GenTot$Years == 2012] <- "2012-13"
# GenTot$Years[GenTot$Years == 2013] <- "2013-14"
# GenTot$Years[GenTot$Years == 2014] <- "2014-15"
# GenTot$Years[GenTot$Years == 2015] <- "2015-16"
# GenTot$Years[GenTot$Years == 2016] <- "2016-17"
# 
# GenTot <- GenTot[c(3,1,2)]
# 
# Genderinfo <- aggregate(.~Years+Gender, data=GenTot, sum)
# options(scipen = 999)
# 
# GenderPlot <- ggplot(Genderinfo, aes(Years,Total)) + labs(title= "California Yearly Suspensions in K-12", subtitle = "By Gender") + geom_bar(aes(fill = Gender),stat="identity") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits=c(0,10000), breaks = seq(0,10000,1000), labels = comma)
# GenderPlot



#Steps to build bar graph for ethnicity
```{r}
#BLACK
county_RBcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RB")

RBcounty11 <- county_RBcount11[c(2:59), c(1,6,10,12)]
RBcounty11

RBcounty11$totalsuspensions <- as.numeric(as.character(RBcounty11$totalsuspensions))
RBcounty11$totalsuspensions[is.na(RBcounty11$totalsuspensions)] <- 0

SuspensionRB11 <- sum(as.numeric(as.character(RBcounty11$totalsuspensions)))
SuspensionRB11

#---------------------------------------------------------------------------------------------------

#American Indian
county_RIcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RI")
RIcounty11 <- county_RIcount11[c(2:59), c(1,6,10,12)]
RIcounty11

RIcounty11$totalsuspensions <- as.numeric(as.character(RIcounty11$totalsuspensions))
RIcounty11$totalsuspensions[is.na(RIcounty11$totalsuspensions)] <- 0

SuspensionRI11 <- sum(as.numeric(as.character(RIcounty11$totalsuspensions)))
SuspensionRI11

#---------------------------------------------------------------------------------------------------

#Asian 
county_RAcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RA")
RAcounty11 <- county_RAcount11[c(2:59), c(1,6,10,12)]
RAcounty11

RAcounty11$totalsuspensions <- as.numeric(as.character(RAcounty11$totalsuspensions))
RAcounty11$totalsuspensions[is.na(RAcounty11$totalsuspensions)] <- 0

SuspensionRA11 <- sum(as.numeric(as.character(RAcounty11$totalsuspensions)))
SuspensionRA11

#---------------------------------------------------------------------------------------------------

#Flipino
county_RFcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RF")
RFcounty11 <- county_RFcount11[c(2:59), c(1,6,10,12)]
RFcounty11

RFcounty11$totalsuspensions <- as.numeric(as.character(RFcounty11$totalsuspensions))
RFcounty11$totalsuspensions[is.na(RFcounty11$totalsuspensions)] <- 0

SuspensionRF11 <- sum(as.numeric(as.character(RFcounty11$totalsuspensions)))
SuspensionRF11

#---------------------------------------------------------------------------------------------------

#Hispanic 
county_RHcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RH")
RHcounty11 <- county_RHcount11[c(2:59), c(1,6,10,12)]
RHcounty11

RHcounty11$totalsuspensions <- as.numeric(as.character(RHcounty11$totalsuspensions))
RHcounty11$totalsuspensions[is.na(RHcounty11$totalsuspensions)] <- 0

SuspensionRH11 <- sum(as.numeric(as.character(RHcounty11$totalsuspensions)))
SuspensionRH11

#--------------------------------------------------------------------------------------------------

#Pacific Islander
county_RPcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RP")
RPcounty11 <- county_RPcount11[c(2:59), c(1,6,10,12)]
RPcounty11

RPcounty11$totalsuspensions <- as.numeric(as.character(RPcounty11$totalsuspensions))
RPcounty11$totalsuspensions[is.na(RPcounty11$totalsuspensions)] <- 0

SuspensionRP11 <- sum(as.numeric(as.character(RPcounty11$totalsuspensions)))
SuspensionRP11

#------------------------------------------------------------------------------------------------

#Two or More Races 
county_RTcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RT")
RTcounty11 <- county_RTcount11[c(2:59), c(1,6,10,12)]
RTcounty11

RTcounty11$totalsuspensions <- as.numeric(as.character(RTcounty11$totalsuspensions))
RTcounty11$totalsuspensions[is.na(RTcounty11$totalsuspensions)] <- 0

SuspensionRT11 <- sum(as.numeric(as.character(RTcounty11$totalsuspensions)))
SuspensionRT11

#-------------------------------------------------------------------------------------------------

#White 
county_RWcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RW")
RWcounty11 <- county_RWcount11[c(2:59), c(1,6,10,12)]
RWcounty11

SuspensionRW11 <- sum(as.numeric(as.character(RWcounty11$totalsuspensions)))
SuspensionRW11

#-------------------------------------------------------------------------------------------------
#NOT REPORTED 
county_RDcount11 <- filter(Suspension11, Suspension11$reportingcategory =="RD")
RDcounty11 <- county_RDcount12[c(2:59), c(1,6,10,12)]
RDcounty11

RDcounty11$totalsuspensions <- as.numeric(as.character(RDcounty11$totalsuspensions))
RDcounty11$totalsuspensions[is.na(RDcounty11$totalsuspensions)] <- 0


SuspensionRD11 <- sum(as.numeric(as.character(RDcounty11$totalsuspensions)))
SuspensionRD11


#-----------------------------------------------------------------------------------------------

#BLACK
county_RBcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RB")

RBcounty12 <- county_RBcount12[c(2:59), c(1,6,10,12)]
RBcounty12

RBcounty12$totalsuspensions <- as.numeric(as.character(RBcounty12$totalsuspensions))
RBcounty12$totalsuspensions[is.na(RBcounty12$totalsuspensions)] <- 0

SuspensionRB12 <- sum(as.numeric(as.character(RBcounty12$totalsuspensions)))
SuspensionRB12

#---------------------------------------------------------------------------------------------------

#American Indian
county_RIcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RI")
RIcounty12 <- county_RIcount12[c(2:59), c(1,6,10,12)]
RIcounty12

RIcounty12$totalsuspensions <- as.numeric(as.character(RIcounty12$totalsuspensions))
RIcounty12$totalsuspensions[is.na(RIcounty12$totalsuspensions)] <- 0

SuspensionRI12 <- sum(as.numeric(as.character(RIcounty12$totalsuspensions)))
SuspensionRI12

#---------------------------------------------------------------------------------------------------

#Asian 
county_RAcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RA")
RAcounty12 <- county_RAcount12[c(2:59), c(1,6,10,12)]
RAcounty12

RAcounty12$totalsuspensions <- as.numeric(as.character(RAcounty12$totalsuspensions))
RAcounty12$totalsuspensions[is.na(RAcounty12$totalsuspensions)] <- 0

SuspensionRA12 <- sum(as.numeric(as.character(RAcounty12$totalsuspensions)))
SuspensionRA12

#---------------------------------------------------------------------------------------------------

#Flipino
county_RFcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RF")
RFcounty12 <- county_RFcount12[c(2:59), c(1,6,10,12)]
RFcounty12

RFcounty12$totalsuspensions <- as.numeric(as.character(RFcounty12$totalsuspensions))
RFcounty12$totalsuspensions[is.na(RFcounty12$totalsuspensions)] <- 0

SuspensionRF12 <- sum(as.numeric(as.character(RFcounty12$totalsuspensions)))
SuspensionRF12

#---------------------------------------------------------------------------------------------------

#Hispanic 
county_RHcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RH")
RHcounty12 <- county_RHcount12[c(2:59), c(1,6,10,12)]
RHcounty12

SuspensionRH12 <- sum(as.numeric(as.character(RHcounty12$totalsuspensions)))
SuspensionRH12

#--------------------------------------------------------------------------------------------------

#Pacific Islander
county_RPcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RP")
RPcounty12 <- county_RPcount12[c(2:59), c(1,6,10,12)]
RPcounty12

RPcounty12$totalsuspensions <- as.numeric(as.character(RPcounty12$totalsuspensions))
RPcounty12$totalsuspensions[is.na(RPcounty12$totalsuspensions)] <- 0

SuspensionRP12 <- sum(as.numeric(as.character(RPcounty12$totalsuspensions)))
SuspensionRP12

#------------------------------------------------------------------------------------------------

#Two or More Races 
county_RTcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RT")
RTcounty12 <- county_RTcount12[c(2:59), c(1,6,10,12)]
RTcounty12

RTcounty12$totalsuspensions <- as.numeric(as.character(RTcounty11$totalsuspensions))
RTcounty12$totalsuspensions[is.na(RTcounty11$totalsuspensions)] <- 0

SuspensionRT12 <- sum(as.numeric(as.character(RTcounty12$totalsuspensions)))
SuspensionRT12

#-------------------------------------------------------------------------------------------------

#White 
county_RWcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RW")
RWcounty12 <- county_RWcount12[c(2:59), c(1,6,10,12)]
RWcounty12

SuspensionRW12 <- sum(as.numeric(as.character(RWcounty12$totalsuspensions)))
SuspensionRW12

#-------------------------------------------------------------------------------------------------

#NOT REPORTED 
county_RDcount12 <- filter(Suspension12, Suspension12$reportingcategory =="RD")
RDcounty12 <- county_RDcount12[c(2:59), c(1,6,10,12)]
RDcounty12

RDcounty12$totalsuspensions <- as.numeric(as.character(RDcounty12$totalsuspensions))
RDcounty12$totalsuspensions[is.na(RDcounty12$totalsuspensions)] <- 0


SuspensionRD12 <- sum(as.numeric(as.character(RDcounty12$totalsuspensions)))
SuspensionRD12

#-------------------------------------------------------------------------------------------------
#BLACK
county_RBcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RB")

RBcounty13 <- county_RBcount13[c(2:59), c(1,6,10,12)]
RBcounty13

RBcounty13$totalsuspensions <- as.numeric(as.character(RBcounty13$totalsuspensions))
RBcounty13$totalsuspensions[is.na(RBcounty13$totalsuspensions)] <- 0

SuspensionRB13 <- sum(as.numeric(as.character(RBcounty13$totalsuspensions)))
SuspensionRB13

#---------------------------------------------------------------------------------------------------

#American Indian
county_RIcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RI")
RIcounty13 <- county_RIcount13[c(2:59), c(1,6,10,12)]
RIcounty13

RIcounty13$totalsuspensions <- as.numeric(as.character(RIcounty13$totalsuspensions))
RIcounty13$totalsuspensions[is.na(RIcounty13$totalsuspensions)] <- 0

SuspensionRI13 <- sum(as.numeric(as.character(RIcounty13$totalsuspensions)))
SuspensionRI13

#---------------------------------------------------------------------------------------------------

#Asian 
county_RAcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RA")
RAcounty13 <- county_RAcount13[c(2:59), c(1,6,10,12)]
RAcounty13

RAcounty13$totalsuspensions <- as.numeric(as.character(RAcounty13$totalsuspensions))
RAcounty13$totalsuspensions[is.na(RAcounty13$totalsuspensions)] <- 0

SuspensionRA13 <- sum(as.numeric(as.character(RAcounty13$totalsuspensions)))
SuspensionRA13

#---------------------------------------------------------------------------------------------------

#Flipino
county_RFcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RF")
RFcounty13 <- county_RFcount13[c(2:59), c(1,6,10,12)]
RFcounty13

RFcounty13$totalsuspensions <- as.numeric(as.character(RFcounty13$totalsuspensions))
RFcounty13$totalsuspensions[is.na(RFcounty13$totalsuspensions)] <- 0

SuspensionRF13 <- sum(as.numeric(as.character(RFcounty13$totalsuspensions)))
SuspensionRF13

#---------------------------------------------------------------------------------------------------

#Hispanic 
county_RHcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RH")
RHcounty13 <- county_RHcount13[c(2:59), c(1,6,10,12)]
RHcounty13

RHcounty13$totalsuspensions <- as.numeric(as.character(RHcounty13$totalsuspensions))
RHcounty13$totalsuspensions[is.na(RHcounty13$totalsuspensions)] <- 0

SuspensionRH13 <- sum(as.numeric(as.character(RHcounty13$totalsuspensions)))
SuspensionRH13

#--------------------------------------------------------------------------------------------------

#Pacific Islander
county_RPcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RP")
RPcounty13 <- county_RPcount12[c(2:59), c(1,6,10,12)]
RPcounty13

RPcounty13$totalsuspensions <- as.numeric(as.character(RPcounty13$totalsuspensions))
RPcounty13$totalsuspensions[is.na(RPcounty13$totalsuspensions)] <- 0

SuspensionRP13 <- sum(as.numeric(as.character(RPcounty13$totalsuspensions)))
SuspensionRP13

#------------------------------------------------------------------------------------------------

#Two or More Races 
county_RTcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RT")
RTcounty13 <- county_RTcount13[c(2:59), c(1,6,10,12)]
RTcounty13

RTcounty13$totalsuspensions <- as.numeric(as.character(RTcounty13$totalsuspensions))
RTcounty13$totalsuspensions[is.na(RTcounty13$totalsuspensions)] <- 0

SuspensionRT13 <- sum(as.numeric(as.character(RTcounty13$totalsuspensions)))
SuspensionRT13

#-------------------------------------------------------------------------------------------------

#White 
county_RWcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RW")
RWcounty13 <- county_RWcount13[c(2:59), c(1,6,10,12)]
RWcounty13

SuspensionRW13 <- sum(as.numeric(as.character(RWcounty13$totalsuspensions)))
SuspensionRW13

#----------------------------------------------------------------------------------------------
#NOT REPORTED 
county_RDcount13 <- filter(Suspension13, Suspension13$reportingcategory =="RD")
RDcounty13 <- county_RDcount13[c(2:59), c(1,6,10,12)]
RDcounty13

RDcounty13$totalsuspensions <- as.numeric(as.character(RDcounty13$totalsuspensions))
RDcounty13$totalsuspensions[is.na(RDcounty13$totalsuspensions)] <- 0


SuspensionRD13 <- sum(as.numeric(as.character(RDcounty13$totalsuspensions)))
SuspensionRD13

#----------------------------------------------------------------------------------------------
#BLACK
county_RBcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RB")

RBcounty14<- county_RBcount14[c(2:59), c(1,6,10,12)]
RBcounty14

RBcounty14$totalsuspensions <- as.numeric(as.character(RBcounty14$totalsuspensions))
RBcounty14$totalsuspensions[is.na(RBcounty14$totalsuspensions)] <- 0

SuspensionRB14 <- sum(as.numeric(as.character(RBcounty14$totalsuspensions)))
SuspensionRB14

#---------------------------------------------------------------------------------------------------

#American Indian
county_RIcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RI")
RIcounty14 <- county_RIcount14[c(2:59), c(1,6,10,12)]
RIcounty14

RIcounty14$totalsuspensions <- as.numeric(as.character(RIcounty14$totalsuspensions))
RIcounty14$totalsuspensions[is.na(RIcounty14$totalsuspensions)] <- 0

SuspensionRI14 <- sum(as.numeric(as.character(RIcounty14$totalsuspensions)))
SuspensionRI14

#---------------------------------------------------------------------------------------------------

#Asian 
county_RAcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RA")
RAcounty14 <- county_RAcount14[c(2:59), c(1,6,10,12)]
RAcounty14

RAcounty14$totalsuspensions <- as.numeric(as.character(RAcounty14$totalsuspensions))
RAcounty14$totalsuspensions[is.na(RAcounty14$totalsuspensions)] <- 0

SuspensionRA14 <- sum(as.numeric(as.character(RAcounty14$totalsuspensions)))
SuspensionRA14

#---------------------------------------------------------------------------------------------------

#Flipino
county_RFcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RF")
RFcounty14 <- county_RFcount14[c(2:59), c(1,6,10,12)]
RFcounty14

RFcounty14$totalsuspensions <- as.numeric(as.character(RFcounty14$totalsuspensions))
RFcounty14$totalsuspensions[is.na(RFcounty14$totalsuspensions)] <- 0

SuspensionRF14 <- sum(as.numeric(as.character(RFcounty14$totalsuspensions)))
SuspensionRF14

#---------------------------------------------------------------------------------------------------

#Hispanic 
county_RHcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RH")
RHcounty14 <- county_RHcount14[c(2:59), c(1,6,10,12)]
RHcounty14

RHcounty14$totalsuspensions <- as.numeric(as.character(RHcounty14$totalsuspensions))
RHcounty14$totalsuspensions[is.na(RHcounty14$totalsuspensions)] <- 0

SuspensionRH14 <- sum(as.numeric(as.character(RHcounty14$totalsuspensions)))
SuspensionRH14

#--------------------------------------------------------------------------------------------------

#Pacific Islander
county_RPcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RP")
RPcounty14 <- county_RPcount12[c(2:59), c(1,6,10,12)]
RPcounty14

RPcounty14$totalsuspensions <- as.numeric(as.character(RPcounty14$totalsuspensions))
RPcounty14$totalsuspensions[is.na(RPcounty14$totalsuspensions)] <- 0

SuspensionRP14 <- sum(as.numeric(as.character(RPcounty14$totalsuspensions)))
SuspensionRP14

#------------------------------------------------------------------------------------------------

#Two or More Races 
county_RTcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RT")
RTcounty14 <- county_RTcount14[c(2:59), c(1,6,10,12)]
RTcounty14

RTcounty14$totalsuspensions <- as.numeric(as.character(RTcounty14$totalsuspensions))
RTcounty14$totalsuspensions[is.na(RTcounty14$totalsuspensions)] <- 0

SuspensionRT14 <- sum(as.numeric(as.character(RTcounty14$totalsuspensions)))
SuspensionRT14

#-------------------------------------------------------------------------------------------------

#White 
county_RWcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RW")
RWcounty14 <- county_RWcount14[c(2:59), c(1,6,10,12)]
RWcounty14

SuspensionRW14 <- sum(as.numeric(as.character(RWcounty14$totalsuspensions)))
SuspensionRW14

#------------------------------------------------------------------------------------------------

#NOT REPORTED
county_RDcount14 <- filter(Suspension14, Suspension14$reportingcategory =="RD")
RDcounty14 <- county_RDcount14[c(2:59), c(1,6,10,12)]
RDcounty14

RDcounty14$totalsuspensions <- as.numeric(as.character(RDcounty14$totalsuspensions))
RDcounty14$totalsuspensions[is.na(RDcounty14$totalsuspensions)] <- 0


SuspensionRD14 <- sum(as.numeric(as.character(RDcounty14$totalsuspensions)))
SuspensionRD14

#--------------------------------------------------------------------------------------------------

#BLACK
county_RBcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RB")

RBcounty15<- county_RBcount15[c(2:59), c(1,6,10,12)]
RBcounty15

RBcounty15$totalsuspensions <- as.numeric(as.character(RBcounty15$totalsuspensions))
RBcounty15$totalsuspensions[is.na(RBcounty15$totalsuspensions)] <- 0

SuspensionRB15 <- sum(as.numeric(as.character(RBcounty15$totalsuspensions)))
SuspensionRB15

#---------------------------------------------------------------------------------------------------

#American Indian
county_RIcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RI")
RIcounty15 <- county_RIcount15[c(2:59), c(1,6,10,12)]
RIcounty15

RIcounty15$totalsuspensions <- as.numeric(as.character(RIcounty15$totalsuspensions))
RIcounty15$totalsuspensions[is.na(RIcounty15$totalsuspensions)] <- 0

SuspensionRI15 <- sum(as.numeric(as.character(RIcounty15$totalsuspensions)))
SuspensionRI15

#---------------------------------------------------------------------------------------------------

#Asian 
county_RAcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RA")
RAcounty15 <- county_RAcount15[c(2:59), c(1,6,10,12)]
RAcounty15

RAcounty15$totalsuspensions <- as.numeric(as.character(RAcounty15$totalsuspensions))
RAcounty15$totalsuspensions[is.na(RAcounty15$totalsuspensions)] <- 0

SuspensionRA15 <- sum(as.numeric(as.character(RAcounty15$totalsuspensions)))
SuspensionRA15

#---------------------------------------------------------------------------------------------------

#Flipino
county_RFcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RF")
RFcounty15 <- county_RFcount15[c(2:59), c(1,6,10,12)]
RFcounty15

RFcounty15$totalsuspensions <- as.numeric(as.character(RFcounty15$totalsuspensions))
RFcounty15$totalsuspensions[is.na(RFcounty15$totalsuspensions)] <- 0

SuspensionRF15 <- sum(as.numeric(as.character(RFcounty15$totalsuspensions)))
SuspensionRF15

#---------------------------------------------------------------------------------------------------

#Hispanic 
county_RHcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RH")
RHcounty15 <- county_RHcount15[c(2:59), c(1,6,10,12)]
RHcounty15

RHcounty15$totalsuspensions <- as.numeric(as.character(RHcounty15$totalsuspensions))
RHcounty15$totalsuspensions[is.na(RHcounty15$totalsuspensions)] <- 0


SuspensionRH15 <- sum(as.numeric(as.character(RHcounty15$totalsuspensions)))
SuspensionRH15

#--------------------------------------------------------------------------------------------------

#Pacific Islander
county_RPcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RP")
RPcounty15 <- county_RPcount15[c(2:59), c(1,6,10,12)]
RPcounty15

RPcounty15$totalsuspensions <- as.numeric(as.character(RPcounty15$totalsuspensions))
RPcounty15$totalsuspensions[is.na(RPcounty15$totalsuspensions)] <- 0

SuspensionRP15 <- sum(as.numeric(as.character(RPcounty15$totalsuspensions)))
SuspensionRP15

#------------------------------------------------------------------------------------------------

#Two or More Races 
county_RTcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RT")
RTcounty15 <- county_RTcount15[c(2:59), c(1,6,10,12)]
RTcounty15

RTcounty15$totalsuspensions <- as.numeric(as.character(RTcounty15$totalsuspensions))
RTcounty15$totalsuspensions[is.na(RTcounty15$totalsuspensions)] <- 0

SuspensionRT15 <- sum(as.numeric(as.character(RTcounty15$totalsuspensions)))
SuspensionRT15

#-------------------------------------------------------------------------------------------------

#White 
county_RWcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RW")
RWcounty15 <- county_RWcount15[c(2:59), c(1,6,10,12)]
RWcounty15

SuspensionRW15 <- sum(as.numeric(as.character(RWcounty15$totalsuspensions)))
SuspensionRW15


#----------------------------------------------------------------------------------------------
#NOT REPORTED

county_RDcount15 <- filter(Suspension15, Suspension15$reportingcategory =="RD")
RDcounty15 <- county_RDcount15[c(2:59), c(1,6,10,12)]
RDcounty15

RDcounty15$totalsuspensions <- as.numeric(as.character(RDcounty15$totalsuspensions))
RDcounty15$totalsuspensions[is.na(RDcounty15$totalsuspensions)] <- 0


SuspensionRD15 <- sum(as.numeric(as.character(RDcounty15$totalsuspensions)))
SuspensionRD15

#-----------------------------------------------------------------------------------------------

#BLACK
county_RBcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RB")

RBcounty16<- county_RBcount16[c(2:59), c(1,6,10,12)]
RBcounty16

RBcounty16$totalsuspensions <- as.numeric(as.character(RBcounty16$totalsuspensions))
RBcounty16$totalsuspensions[is.na(RBcounty16$totalsuspensions)] <- 0

SuspensionRB16 <- sum(as.numeric(as.character(RBcounty16$totalsuspensions)))
SuspensionRB16

#---------------------------------------------------------------------------------------------------

#American Indian
county_RIcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RI")
RIcounty16 <- county_RIcount16[c(2:59), c(1,6,10,12)]
RIcounty16

RIcounty16$totalsuspensions <- as.numeric(as.character(RIcounty16$totalsuspensions))
RIcounty16$totalsuspensions[is.na(RIcounty16$totalsuspensions)] <- 0

SuspensionRI16 <- sum(as.numeric(as.character(RIcounty16$totalsuspensions)))
SuspensionRI16

#---------------------------------------------------------------------------------------------------

#Asian 
county_RAcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RA")
RAcounty16 <- county_RAcount16[c(2:59), c(1,6,10,12)]
RAcounty16

RAcounty16$totalsuspensions <- as.numeric(as.character(RAcounty16$totalsuspensions))
RAcounty16$totalsuspensions[is.na(RAcounty16$totalsuspensions)] <- 0

SuspensionRA16 <- sum(as.numeric(as.character(RAcounty16$totalsuspensions)))
SuspensionRA16

#---------------------------------------------------------------------------------------------------

#Flipino
county_RFcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RF")
RFcounty16 <- county_RFcount16[c(2:59), c(1,6,10,12)]
RFcounty16

RFcounty16$totalsuspensions <- as.numeric(as.character(RFcounty16$totalsuspensions))
RFcounty16$totalsuspensions[is.na(RFcounty16$totalsuspensions)] <- 0

SuspensionRF16 <- sum(as.numeric(as.character(RFcounty16$totalsuspensions)))
SuspensionRF16

#---------------------------------------------------------------------------------------------------

#Hispanic 
county_RHcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RH")
RHcounty16 <- county_RHcount16[c(2:59), c(1,6,10,12)]
RHcounty16

RHcounty16$totalsuspensions <- as.numeric(as.character(RHcounty16$totalsuspensions))
RHcounty16$totalsuspensions[is.na(RHcounty16$totalsuspensions)] <- 0


SuspensionRH16 <- sum(as.numeric(as.character(RHcounty16$totalsuspensions)))
SuspensionRH16

#--------------------------------------------------------------------------------------------------

#Pacific Islander
county_RPcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RP")
RPcounty16 <- county_RPcount16[c(2:59), c(1,6,10,12)]
RPcounty16

RPcounty16$totalsuspensions <- as.numeric(as.character(RPcounty16$totalsuspensions))
RPcounty16$totalsuspensions[is.na(RPcounty16$totalsuspensions)] <- 0

SuspensionRP16 <- sum(as.numeric(as.character(RPcounty16$totalsuspensions)))
SuspensionRP16

#------------------------------------------------------------------------------------------------

#Two or More Races 
county_RTcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RT")
RTcounty16 <- county_RTcount16[c(2:59), c(1,6,10,12)]
RTcounty16

RTcounty16$totalsuspensions <- as.numeric(as.character(RTcounty16$totalsuspensions))
RTcounty16$totalsuspensions[is.na(RTcounty16$totalsuspensions)] <- 0

SuspensionRT16 <- sum(as.numeric(as.character(RTcounty16$totalsuspensions)))
SuspensionRT16

#-------------------------------------------------------------------------------------------------

#White 
county_RWcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RW")
RWcounty16 <- county_RWcount16[c(2:59), c(1,6,10,12)]
RWcounty16

SuspensionRW16 <- sum(as.numeric(as.character(RWcounty16$totalsuspensions)))
SuspensionRW16

#-------------------------------------------------------------------------------------------------

#not rported 
county_RDcount16 <- filter(Suspension16, Suspension16$reportingcategory =="RD")
RDcounty16 <- county_RDcount16[c(2:59), c(1,6,10,12)]
RDcounty16

RDcounty16$totalsuspensions <- as.numeric(as.character(RDcounty16$totalsuspensions))
RDcounty16$totalsuspensions[is.na(RDcounty16$totalsuspensions)] <- 0


SuspensionRD16 <- sum(as.numeric(as.character(RDcounty16$totalsuspensions)))
SuspensionRD16
```

#Plotting the bar graphs for Ethnicity 

```{r}
RAethnicity  <-c(SuspensionRA11, SuspensionRA12,SuspensionRA13, SuspensionRA14, SuspensionRA15, SuspensionRA16)

RBethnicity2  <-c(SuspensionRB11, SuspensionRB12,SuspensionRB13, SuspensionRB14, SuspensionRB15, SuspensionRB16)

RHethnicity5  <-c(SuspensionRH11, SuspensionRH12,SuspensionRH13, SuspensionRH14, SuspensionRH15, SuspensionRH16)

RWethnicity8  <-c(SuspensionRW11, SuspensionRW12,SuspensionRW13, SuspensionRW14, SuspensionRW15, SuspensionRW16)

ROsum11  <-sum(SuspensionRF11, SuspensionRP11,SuspensionRT11,SuspensionRI11, SuspensionRD11)

ROsum12  <-sum(SuspensionRF12, SuspensionRP12,SuspensionRT12,SuspensionRI12, SuspensionRD12)

ROsum13  <-sum(SuspensionRF13, SuspensionRP13,SuspensionRT13,SuspensionRI13, SuspensionRD13)

ROsum14 <- sum(SuspensionRF14, SuspensionRP14,SuspensionRT14,SuspensionRI14, SuspensionRD14)

ROsum15 <- sum(SuspensionRF15, SuspensionRP15,SuspensionRT15,SuspensionRI15, SuspensionRD15)

ROsum16 <- sum(SuspensionRF16, SuspensionRP16,SuspensionRT16,SuspensionRI16, SuspensionRD16)

ROethnicity <- c(ROsum11,ROsum12,ROsum13,ROsum14,ROsum15,ROsum16)

Years <- c(2011:2016)

RATot <- data.frame(Years, RAethnicity)
names(RATot) <- c("Years","Total")
RATot$ethnicity <- "Asian"

RBTot <- data.frame(Years, RBethnicity2)
names(RBTot) <- c("Years","Total")
RBTot$ethnicity <- "Black"

RHTot <- data.frame(Years, RHethnicity5)
names(RHTot) <- c("Years","Total")
RHTot$ethnicity <- "Hispanic/Latinx"

RWTot <- data.frame(Years, RWethnicity8)
names(RWTot) <- c("Years","Total")
RWTot$ethnicity <- "White"

ROTot <- data.frame(Years, ROethnicity)
names(ROTot) <- c("Years","Total")
ROTot$ethnicity <- "Other"

EthTot <- rbind(RATot, RBTot, RHTot,RWTot,ROTot )

EthTot$Years[EthTot$Years == 2011] <- "2011-12"
EthTot$Years[EthTot$Years == 2012] <- "2012-13"
EthTot$Years[EthTot$Years == 2013] <- "2013-14"
EthTot$Years[EthTot$Years == 2014] <- "2014-15"
EthTot$Years[EthTot$Years == 2015] <- "2015-16"
EthTot$Years[EthTot$Years == 2016] <- "2016-17"

library(dplyr)
library(scales)
EthTot <- EthTot[c(3,1,2)]

Ethinfo <- aggregate(.~Years+ethnicity, data=EthTot, sum)
options(scipen = 999)

EthPlot <- ggplot(Ethinfo, aes(Years,Total)) + labs(title= "California Yearly Suspensions in K-12 Schools", subtitle = "By Race/Ethnicity") + geom_bar(aes(fill = ethnicity),stat="identity") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits=c(0,750000), breaks = seq(0,750000,75000), labels = comma)
EthPlot

```












